---
title: "Low-depth Illumina polishing Hybracter"
date: "2024-01-22"
author: "Ryan Wick, George Bouras"
output:
  html_document:
    pandoc_args: ["+RTS", "-K64m", "-RTS", "--self-contained",]
    df_print: paged
    keep_md: false
    toc: true
    toc_float: true
    code_folding: hide
---
```{r collapse=TRUE}
library(tidyverse)
library(knitr)
library(readr)
library(dplyr)
library(cowplot)

plot_dir <- "plots"
dir.create(plot_dir)

opts_chunk$set(dpi=300, fig.path='plots/', echo=TRUE, dev=c('png','pdf'), warning=FALSE, message=FALSE)
pdf.options(useDingbats = FALSE)
```


Load data from `results.tsv` and process it a bit. I add a column which contains the number of errors in the draft (pre-Illumina-polish) genomes.

```{r load_data}
per_genome_results <- read_delim("results.tsv", delim = "\t", 
                                 escape_double = FALSE, 
                                 trim_ws = TRUE)

'%ni%' <- Negate('%in%')

# due to non-deterministic error in assembly for Listeria 36/50
per_genome_results <- per_genome_results %>%  filter(genome %ni% c("ATCC_35897_Listeria_welshimeri"))

# 13 instances for E coli, 1 for monocytogenes
structural_errors <-  per_genome_results %>% filter(remaining_errors > 50 )

# filter structural errors out

per_genome_results <- per_genome_results %>% filter(remaining_errors < 50 )

```

Make Hybracter Error Plots per Genome

```{r per genome last plot}



generate_plot <- function(genome_name, long_only_trycycler_threshold, atcc_name,
                          italics_name
                          ) {
  
  ymax <- max(per_genome_results  %>% 
                filter(genome == genome_name) %>%  
                pull(remaining_errors)) + 2
  
  p <- ggplot(per_genome_results %>% 
                filter(polishing == "hybracter_last") %>% 
                filter(genome == genome_name), 
              aes(x=target_illumina_depth, y=remaining_errors ) ) +
    geom_hline(yintercept = long_only_trycycler_threshold, 
               color="#004488", linetype = "dashed") +
    geom_point(color="#662929", size=1.25) + 
    theme_bw() +
    scale_x_continuous(limits = c(0, 50), expand = c(0, 0)) +
    scale_y_continuous(limits = c(0, ymax), expand = c(0, 0),
                       breaks = function(x) unique(floor(pretty(seq(min(x), (max(x) + 1) * 1.1))))) +
    labs(title= bquote(.(atcc_name) ~ italic(.(italics_name))) , x="Illumina depth", y="Errors")
  
  return(p)
}




```

```{r plots}

se_plot <- generate_plot("ATCC_10708_Salmonella_enterica", 3, "ATCC 10708", "Salmonella enterica")
vp_plot <- generate_plot("ATCC_17802_Vibrio_parahaemolyticus", 2, "ATCC 17802", "Vibrio parahaemolyticus")
li_plot <- generate_plot("ATCC_19119_Listeria_ivanovii", 5, "ATCC 19119", "Listeria ivanovii")
ec_plot <- generate_plot("ATCC_25922_Escherichia_coli", 1, "ATCC 25922", "Escherichia coli")
cl_plot <- generate_plot("ATCC_35221_Campylobacter_lari", 18, "ATCC 35221", "Campylobacter lari")
cj_plot <- generate_plot("ATCC_33560_Campylobacter_jejuni", 5, "ATCC 33560", "Campylobacter jejuni")
lm_plot <- generate_plot("ATCC_BAA-679_Listeria_monocytogenes", 0, "ATCC BAA-679", "Listeria monocytogenes")


jpeg(file = paste(plot_dir, "Supp_Figure6.jpeg", sep = "/" ), units = "in", 
     width = 9, 
     height = 16, bg = "transparent", res = 600)


plot_grid(se_plot, vp_plot, 
          li_plot, ec_plot, cl_plot, cj_plot, 
          lm_plot, nrow=4, align = 'hv')
dev.off()



```


Make a dataframe with the error counts totaled over all 7 genomes (excluding the depths where E. coli and L. monocytogenes have problems with the automated Flye long read assemblies). Didn't actually end up including this.

```{r totals}
total_results <- per_genome_results %>%
  filter(polishing == "hybracter_last") %>% 
  group_by(target_illumina_depth) %>%
  summarise(total_hybracter_errors = sum(remaining_errors),
            count = n()) %>% 
  filter(count == 7)

ymax <- 100
  
  
  p <- ggplot(total_results, 
              aes(x=target_illumina_depth, 
                  y=total_hybracter_errors ) ) +
    geom_point(color="#662929", size=1.25) + 
    geom_hline(yintercept = 34, 
               color="#004488", linetype = "dashed") +
    theme_bw() +
    scale_x_continuous(limits = c(0, 50), expand = c(0, 0)) +
    scale_y_continuous(limits = c(0, ymax), expand = c(0, 0),
                       breaks = function(x) unique(floor(pretty(seq(min(x), (max(x) + 1) * 1.1))))) +
    labs(title= "Total Hybracter Errors for 7 Genomes Without Assembly Heterogeneity", x="Illumina depth", y="Errors")


  
```

Look at where Hybracter Best (aka the intermediate assemblies ALE score highest) and Hybracter Last differ - Best is never better than Last, and often worse. It will be worse where ALE thinks an assembly before Pypolca polishing is better than the Pypolca polished version. 


```{r per genome comp plot}


generate_comp_plot <- function(df,genome_name, long_only_trycycler_threshold, atcc_name,
                          italics_name, legend_flag
                          ) {
  
  df$polishing <- gsub("hybracter_last", "Last (Post-polishing)", df$polishing)
  df$polishing <- gsub("hybracter_best", "Best (ALE)", df$polishing)
  
  ymax <- max(df  %>% 
                filter(genome == genome_name) %>%  
                pull(remaining_errors)) + 2
  
  p <- ggplot(df %>% 
                filter(genome == genome_name), 
              aes(x=target_illumina_depth, y=remaining_errors, color = polishing ) ) +
    geom_hline(yintercept = long_only_trycycler_threshold, 
               color="#004488", linetype = "dashed") +
    geom_point( size=1.25) + 
    theme_bw() +
    scale_x_continuous(limits = c(0, 50), expand = c(0, 0)) +
    scale_y_continuous(limits = c(0, ymax), expand = c(0, 0)) +
    labs(title= bquote(.(atcc_name) ~ italic(.(italics_name))) , x="Illumina depth", y="Errors") + 
          scale_color_manual(name = "Hybracter Logic Method",
                       labels = c("Best (ALE)", 
                                  "Last (Post-polishing)"),
                       values = c("Best (ALE)" = "#99D6D6", 
                                  "Last (Post-polishing)" = "#662929"))  # Adjust colors as needed
  
    if(legend_flag) {
      p <- p
    } else {
        p <- p + guides(color = FALSE)  # Hide the color legend if legend_flag is FALSE
    }

  
  return(p)
}




```

```{r plots}

se_plot_w_legend <- generate_comp_plot(per_genome_results, "ATCC_10708_Salmonella_enterica", 3, "ATCC 10708", "Salmonella enterica", TRUE) 

se_plot_w_legend <- se_plot_w_legend + 
  geom_point( size=3) +
          scale_fill_manual(name = "Hybracter Logic Method",
                       labels = c("Best (ALE)", 
                                  "Last (Post-polishing)"),
                       values = c("Best (ALE)" = "#99D6D6", 
                                  "Last (Post-polishing)" = "#662929"))+
  theme(
    legend.title = element_text(size = 22),  # Adjust title size
    legend.text = element_text(size = 16)     # Adjust label size
  ) 

se_plot <- generate_comp_plot(per_genome_results, "ATCC_10708_Salmonella_enterica", 3, "ATCC 10708", "Salmonella enterica", FALSE)

vp_plot <- generate_comp_plot(per_genome_results, "ATCC_17802_Vibrio_parahaemolyticus", 2, "ATCC 17802", "Vibrio parahaemolyticus", FALSE)
li_plot <- generate_comp_plot(per_genome_results, "ATCC_19119_Listeria_ivanovii", 5, "ATCC 19119", "Listeria ivanovii", FALSE)
ec_plot <- generate_comp_plot(per_genome_results, "ATCC_25922_Escherichia_coli", 1, "ATCC 25922", "Escherichia coli", FALSE)
cl_plot <- generate_comp_plot(per_genome_results, "ATCC_35221_Campylobacter_lari", 18, "ATCC 35221", "Campylobacter lari", FALSE)
cj_plot <- generate_comp_plot(per_genome_results, "ATCC_33560_Campylobacter_jejuni", 5, "ATCC 33560", "Campylobacter jejuni", FALSE)
lm_plot <- generate_comp_plot(per_genome_results, "ATCC_BAA-679_Listeria_monocytogenes", 0, "ATCC BAA-679", "Listeria monocytogenes", FALSE)


legend_plot <- cowplot::get_legend(se_plot_w_legend)

grid <- plot_grid(
  se_plot, vp_plot, 
  li_plot, ec_plot, 
  cl_plot, cj_plot, 
  lm_plot, legend_plot, 
  nrow = 4, align = 'hv'
)



jpeg(file = paste(plot_dir, "SuppFig4.jpeg", sep = "/" ), units = "in", 
     width = 9, 
     height = 16, bg = "transparent", res = 600)

grid

dev.off()



```

