---
title: "Low-depth Illumina polishing"
date: "2024-01-22"
author: "Ryan Wick"
output:
  html_document:
    pandoc_args: ["+RTS", "-K64m", "-RTS", "--self-contained",]
    df_print: paged
    keep_md: false
    toc: true
    toc_float: true
    code_folding: hide
---
```{r collapse=TRUE}
library(tidyverse)
library(knitr)
library(readr)
library(dplyr)
library(cowplot)

opts_chunk$set(dpi=300, fig.path='plots/', echo=TRUE, dev=c('png','pdf'), warning=FALSE, message=FALSE)
pdf.options(useDingbats = FALSE)
```


Load data from `results.tsv` and process it a bit. I add a column which contains the number of errors in the draft (pre-Illumina-polish) genomes:
```{r load_data}
per_genome_results <- read_delim("results.tsv", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(per_genome_results) <- c("genome", "depth", "polishing", "errors")
per_genome_results$depth <- as.numeric(per_genome_results$depth)
per_genome_results <- per_genome_results %>% pivot_wider(names_from = polishing, values_from = errors)

per_genome_results <- per_genome_results %>%
  mutate(before_polish = case_when(
    genome == "ATCC_10708_Salmonella_enterica" ~ 3,
    genome == "ATCC_14035_Vibrio_cholerae" ~ 2,
    genome == "ATCC_17802_Vibrio_parahaemolyticus" ~ 2,
    genome == "ATCC_19119_Listeria_ivanovii" ~ 5,
    genome == "ATCC_25922_Escherichia_coli" ~ 1,
    genome == "ATCC_33560_Campylobacter_jejuni" ~ 5,
    genome == "ATCC_35221_Campylobacter_lari" ~ 18,
    genome == "ATCC_35897_Listeria_welshimeri" ~ 1,
    genome == "ATCC_BAA-679_Listeria_monocytogenes" ~ 0))
```

Make a dataframe with the error counts totalled over all nine genomes:
```{r totals}
total_results <- per_genome_results %>%
  group_by(depth) %>%
  summarise(before_polish = sum(before_polish),
            polypolish_errors = sum(Polypolish),
            polypolish_careful_errors = sum(`Polypolish-careful`),
            pypolca_errors = sum(pypolca),
            pypolca_careful_errors = sum(`pypolca-careful`),
            hypo_errors = sum(HyPo),
            fmlrc2_errors = sum(FMLRC2),
            nextpolish_errors = sum(NextPolish),
            pilon_errors = sum(Pilon),
            polypolish_pypolca_errors = sum(`Polypolish+pypolca`),
            polypolish_careful_pypolca_careful_errors = sum(`Polypolish-careful+pypolca-careful`),
            polypolish_careful_pypolca_errors = sum(`Polypolish-careful+pypolca`),
            polypolish_pypolca_careful_errors = sum(`Polypolish+pypolca-careful`),
            pypolca_polypolish_errors = sum(`pypolca+Polypolish`),
            pypolca_careful_polypolish_careful_errors = sum(`pypolca-careful+Polypolish-careful`),
            pypolca_careful_polypolish_errors = sum(`pypolca-careful+Polypolish`),
            pypolca_polypolish_careful_errors = sum(`pypolca+Polypolish-careful`))
```

Plot the total errors vs Illumina depth for each polisher and polisher combination. These plots cap the y-axis at 45 and indicate peak errors with text as necessary:
```{r single_tool_plots, fig.width = 10, fig.height = 12}
plot_to_45 <- function(column_name, polisher_name) {
  peak_index <- which.max(total_results[[column_name]])
  peak_errors <- total_results[[column_name]][peak_index]
  peak_depth <- total_results$depth[peak_index]
  peak_label = paste("peak:\n", peak_errors, " errors", sep="")
  p <- ggplot(total_results, aes(x=depth, y=!!sym(column_name))) +
    geom_hline(yintercept = 37, color="darkblue", linetype = "dashed") +
    geom_point(color="darkslategray") + 
    theme_bw() +
    scale_x_continuous(limits = c(0, 50), expand = c(0, 0)) +
    scale_y_continuous(limits = c(0, 45), expand = c(0, 0)) +
    labs(title=polisher_name, x="Illumina depth", y="Errors")
  if (peak_errors > 45) {
    p <- p +
      annotate("text", label=peak_label, x=7.5, y=41.3, colour="darkred", lineheight = 0.9)
  }
  return(p)
}

p1 <- plot_to_45("polypolish_errors", "Polypolish-defaults")
p2 <- plot_to_45("pypolca_errors", "pypolca-defaults")
p3 <- plot_to_45("polypolish_careful_errors", "Polypolish-careful")
p4 <- plot_to_45("pypolca_careful_errors", "pypolca-careful")
p5 <- plot_to_45("fmlrc2_errors", "FMLRC2")
p6 <- plot_to_45("hypo_errors", "HyPo")
p7 <- plot_to_45("nextpolish_errors", "NextPolish")
p8 <- plot_to_45("pilon_errors", "Pilon")

plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, nrow=4)
```
```{r polypolish_pypolca_combinations, fig.width = 10, fig.height = 12}
p1 <- plot_to_45("polypolish_pypolca_errors", "Polypolish-defaults + pypolca-defaults")
p2 <- plot_to_45("pypolca_polypolish_errors", "pypolca-defaults + Polypolish-defaults")
p3 <- plot_to_45("polypolish_careful_pypolca_errors", "Polypolish-careful + pypolca-defaults")
p4 <- plot_to_45("pypolca_polypolish_careful_errors", "pypolca-defaults + Polypolish-careful")
p5 <- plot_to_45("polypolish_pypolca_careful_errors", "Polypolish-defaults + pypolca-careful")
p6 <- plot_to_45("pypolca_careful_polypolish_errors", "pypolca-careful + Polypolish-defaults")
p7 <- plot_to_45("polypolish_careful_pypolca_careful_errors", "Polypolish-careful + pypolca-careful")
p8 <- plot_to_45("pypolca_careful_polypolish_careful_errors", "pypolca-careful + Polypolish-careful")

plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, nrow=4)
```

For the polishers/combinations that exceed 45 total errors, plot them with their full range:
```{r plot_full_range, fig.width = 8, fig.height = 5}
plot_full_range <- function(column_name, polisher_name) {
  title <- paste("Total errors after", polisher_name)
  max_y <- max(total_results[[column_name]], na.rm = TRUE) * 1.05
  p <- ggplot(total_results, aes(x=depth, y=!!sym(column_name))) +
    geom_hline(yintercept = 37, color="darkblue", linetype = "dashed") +
    geom_point(color="darkslategray") +
    theme_bw() +
    scale_x_continuous(limits = c(0, 50), expand = c(0, 0)) +
    scale_y_continuous(limits = c(0, max_y), expand = c(0, 0)) +
    labs(title=title, x="Illumina depth", y="Errors")
  return(p)
}

plot_full_range("pypolca_errors", "pypolca-defaults")
plot_full_range("hypo_errors", "HyPo")
plot_full_range("fmlrc2_errors", "FMLRC2")
plot_full_range("nextpolish_errors", "NextPolish")
plot_full_range("pilon_errors", "Pilon")

plot_full_range("polypolish_pypolca_errors", "Polypolish-defaults + pypolca-defaults")
plot_full_range("polypolish_careful_pypolca_errors", "Polypolish --careful + pypolca-defaults")
plot_full_range("pypolca_polypolish_errors", "pypolca-defaults + Polypolish-defaults")
plot_full_range("pypolca_polypolish_careful_errors", "pypolca-defaults + Polypolish --careful")
```

For each individual polisher, count how many times it made an input assembly better/worse and draw a stacked-bar plot:
```{r better_or_worse, fig.width = 8, fig.height = 4.5}
count_results <- function(tool_name, data) {
  tibble(
    Tool = tool_name,
    better = nrow(data %>% filter(!!sym(tool_name) < before_polish)),
    same = nrow(data %>% filter(!!sym(tool_name) == before_polish)),
    worse = nrow(data %>% filter(!!sym(tool_name) > before_polish))
  )
}

made_better_or_worse <- map_dfr(c("Polypolish", "Polypolish-careful", "pypolca", "pypolca-careful", "HyPo", "FMLRC2", "NextPolish", "Pilon"),
                                count_results, data = per_genome_results)

made_better_or_worse <- made_better_or_worse %>%
  pivot_longer(cols = -Tool, names_to = "Outcome", values_to = "Count") %>%
  mutate(Outcome = factor(Outcome, levels = c("better", "same", "worse"))) %>%
  mutate(Tool = factor(Tool, levels = c("Polypolish", "Polypolish-careful", "pypolca", "pypolca-careful", "FMLRC2", "HyPo", "NextPolish", "Pilon")))

# Create the stacked-bar plot
ggplot(made_better_or_worse, aes(x = Tool, y = Count, fill = Outcome)) +
  geom_bar(stat = "identity") +
  labs(title = "Polishing tools by outcome", x = NULL, y = "Genome count") +
  theme_bw() +
  scale_fill_manual(values = c("better" = "#74add1",
                               "same" = "#ffffbf",
                               "worse" = "#f46d43")) +
  scale_y_continuous(expand = c(0, 0)) + 
  scale_x_discrete(labels = c("Polypolish-\ndefaults", "Polypolish-\ncareful", "pypolca-\ndefaults", "pypolca\n-careful", "FMLRC2", "HyPo", "NextPolish", "Pilon"))
```

For each depth range (groups of 10x), determine which polisher/combination gave the best overall results:
```{r depth_groups}
best_by_depth_range <- function(total_results, min_depth, max_depth) {
  results_by_depth <- total_results %>% filter(depth > min_depth & depth <= max_depth)
  results_by_depth <- results_by_depth
  best_results <- results_by_depth %>%
    select(-depth) %>%
    summarise_all(sum) %>%
    pivot_longer(cols = everything(), names_to = "tool", values_to = "sum") %>%
    filter(sum == min(sum))
  return(best_results$tool)
}

interval <- 10
for (min_depth in seq(0, 45, interval)) {
  max_depth <- min_depth + interval
  best_tools <- best_by_depth_range(total_results, min_depth, max_depth)
  best_tools <- paste(best_tools, collapse = ", ")
  best_tools <- str_replace_all(best_tools, "_errors", "")
  cat(min_depth, "-", max_depth, ": ", best_tools, "\n", sep="")
}
```
