---
title: "Low-depth Illumina polishing"
date: "2024-02-29"
author: "Ryan Wick, George Bouras"
output:
  html_document:
    pandoc_args: ["+RTS", "-K64m", "-RTS", "--self-contained",]
    df_print: paged
    keep_md: false
    toc: true
    toc_float: true
    code_folding: hide
---
```{r collapse=TRUE}
library(tidyverse)
library(knitr)
library(readr)
library(dplyr)
library(cowplot)

plot_dir <- "plots"
dir.create(plot_dir)

opts_chunk$set(dpi=300, fig.path='plots/', echo=TRUE, dev=c('png','pdf'), warning=FALSE, message=FALSE)
pdf.options(useDingbats = FALSE)
```


Load data from `results.tsv` and process it a bit. I add a column which contains the number of errors in the draft (pre-Illumina-polish) genomes:
```{r load_data}
per_genome_results <- read_delim("results.tsv", delim = "\t", escape_double = FALSE, trim_ws = TRUE)
colnames(per_genome_results) <- c("genome", "depth", "polishing", "errors")
per_genome_results$depth <- as.numeric(per_genome_results$depth)
per_genome_results <- per_genome_results %>% pivot_wider(names_from = polishing, values_from = errors)

per_genome_results <- per_genome_results %>%
  mutate(before_polish = case_when(
    genome == "ATCC_10708_Salmonella_enterica" ~ 3,
    genome == "ATCC_14035_Vibrio_cholerae" ~ 2,
    genome == "ATCC_17802_Vibrio_parahaemolyticus" ~ 2,
    genome == "ATCC_19119_Listeria_ivanovii" ~ 5,
    genome == "ATCC_25922_Escherichia_coli" ~ 1,
    genome == "ATCC_33560_Campylobacter_jejuni" ~ 5,
    genome == "ATCC_35221_Campylobacter_lari" ~ 18,
    genome == "ATCC_35897_Listeria_welshimeri" ~ 1,
    genome == "ATCC_BAA-679_Listeria_monocytogenes" ~ 0))
```

Make a dataframe with the error counts totalled over all nine genomes:
```{r totals}
introduced <- per_genome_results
introduced$Polypolish_introduced <- ifelse(introduced$Polypolish - introduced$before_polish > 0, TRUE, FALSE)
introduced$`Polypolish-careful_introduced` <- ifelse(introduced$`Polypolish-careful` - introduced$before_polish > 0, TRUE, FALSE)
introduced$pypolca_introduced <- ifelse(introduced$pypolca - introduced$before_polish > 0, TRUE, FALSE)
introduced$`pypolca-careful_introduced` <- ifelse(introduced$`pypolca-careful` - introduced$before_polish > 0, TRUE, FALSE)
introduced$HyPo_introduced <- ifelse(introduced$HyPo - introduced$before_polish > 0, TRUE, FALSE)
introduced$FMLRC2_introduced <- ifelse(introduced$FMLRC2 - introduced$before_polish > 0, TRUE, FALSE)
introduced$NextPolish_introduced <- ifelse(introduced$NextPolish - introduced$before_polish > 0, TRUE, FALSE)
introduced$Pilon_introduced <- ifelse(introduced$Pilon - introduced$before_polish > 0, TRUE, FALSE)
introduced$`Polypolish+pypolca_introduced` <- ifelse(introduced$`Polypolish+pypolca` - introduced$before_polish > 0, TRUE, FALSE)
introduced$`Polypolish-careful+pypolca-careful_introduced` <- ifelse(introduced$`Polypolish-careful+pypolca-careful` - introduced$before_polish > 0, TRUE, FALSE)
introduced$`Polypolish-careful+pypolca_introduced` <- ifelse(introduced$`Polypolish-careful+pypolca` - introduced$before_polish > 0, TRUE, FALSE)
introduced$`Polypolish+pypolca-careful_introduced` <- ifelse(introduced$`Polypolish+pypolca-careful` - introduced$before_polish > 0, TRUE, FALSE)
introduced$`pypolca+Polypolish_introduced` <- ifelse(introduced$`pypolca+Polypolish` - introduced$before_polish > 0, TRUE, FALSE)
introduced$`pypolca-careful+Polypolish-careful_introduced` <- ifelse(introduced$`pypolca-careful+Polypolish-careful` - introduced$before_polish > 0, TRUE, FALSE)
introduced$`pypolca-careful+Polypolish_introduced` <- ifelse(introduced$`pypolca-careful+Polypolish` - introduced$before_polish > 0, TRUE, FALSE)
introduced$`pypolca+Polypolish-careful_introduced` <- ifelse(introduced$`pypolca+Polypolish-careful` - introduced$before_polish > 0, TRUE, FALSE)

total_results <- introduced %>%
  group_by(depth) %>%
  summarise(before_polish = sum(before_polish),
            polypolish_errors = sum(Polypolish),
            polypolish_introduced = any(Polypolish_introduced),
            polypolish_careful_errors = sum(`Polypolish-careful`),
            polypolish_careful_introduced = any(`Polypolish-careful_introduced`),
            pypolca_errors = sum(pypolca),
            pypolca_introduced = any(pypolca_introduced),
            pypolca_careful_errors = sum(`pypolca-careful`),
            pypolca_careful_introduced = any(`pypolca-careful_introduced`),
            hypo_errors = sum(HyPo),
            hypo_introduced = any(HyPo_introduced),
            fmlrc2_errors = sum(FMLRC2),
            fmlrc2_introduced = any(FMLRC2_introduced),
            nextpolish_errors = sum(NextPolish),
            nextpolish_introduced = any(NextPolish_introduced),
            pilon_errors = sum(Pilon),
            pilon_introduced = any(Pilon_introduced),
            polypolish_pypolca_errors = sum(`Polypolish+pypolca`),
            polypolish_pypolca_introduced = any(`Polypolish+pypolca_introduced`),
            polypolish_careful_pypolca_careful_errors = sum(`Polypolish-careful+pypolca-careful`),
            polypolish_careful_pypolca_careful_introduced = any(`Polypolish-careful+pypolca-careful_introduced`),
            polypolish_careful_pypolca_errors = sum(`Polypolish-careful+pypolca`),
            polypolish_careful_pypolca_introduced = any(`Polypolish-careful+pypolca_introduced`),
            polypolish_pypolca_careful_errors = sum(`Polypolish+pypolca-careful`),
            polypolish_pypolca_careful_introduced = any(`Polypolish+pypolca-careful_introduced`),
            pypolca_polypolish_errors = sum(`pypolca+Polypolish`),
            pypolca_polypolish_introduced = any(`pypolca+Polypolish_introduced`),
            pypolca_careful_polypolish_careful_errors = sum(`pypolca-careful+Polypolish-careful`),
            pypolca_careful_polypolish_careful_introduced = any(`pypolca-careful+Polypolish-careful_introduced`),
            pypolca_careful_polypolish_errors = sum(`pypolca-careful+Polypolish`),
            pypolca_careful_polypolish_introduced = any(`pypolca-careful+Polypolish_introduced`),
            pypolca_polypolish_careful_errors = sum(`pypolca+Polypolish-careful`),
            pypolca_polypolish_careful_introduced = any(`pypolca+Polypolish-careful_introduced`))
```


```{r totals}
introduced_df <- introduced

colnames(introduced_df) <- gsub("_introduced", "_overall_decreased_accuracy", colnames(introduced_df) )

write.csv(introduced_df, file = "all_depths_errors.csv")


```

Plot the total errors vs Illumina depth for each polisher and polisher combination. These plots cap the y-axis at 45 and indicate peak errors with text as necessary:
```{r single_tool_plots, fig.width = 10, fig.height = 12}
plot_to_45 <- function(column_name, polisher_name, no_x = FALSE, no_y = FALSE, include_colour = FALSE) {
  if (include_colour) {
    colours <- scale_colour_manual(values = c("TRUE" = "#CC0000", "FALSE" = "#127EAD"))
  } else {
    colours <- scale_colour_manual(values = c("TRUE" = "#662929", "FALSE" = "#662929"))
  }
  introduced_column <- gsub("_errors", "_introduced", column_name)
  peak_index <- which.max(total_results[[column_name]])
  peak_errors <- total_results[[column_name]][peak_index]
  peak_depth <- total_results$depth[peak_index]
  peak_label = paste("peak:\n", peak_errors, " errors", sep="")
  p <- ggplot(total_results, aes(x=depth, y=!!sym(column_name), colour=!!sym(introduced_column) )) +
    geom_hline(yintercept = 37, color="#3A3A3A", linetype = "dashed") +
    geom_point(size=1.25) + colours +
    theme_bw() + theme(legend.position = "none") +
    scale_x_continuous(limits = c(0, 50), expand = c(0, 0)) +
    scale_y_continuous(limits = c(0, 45), expand = c(0, 0)) +
    labs(title=polisher_name, x="Illumina depth", y="Errors")
  if (peak_errors > 45) {
    p <- p + annotate("text", label=peak_label, x=7.5, y=41.3, colour="#AF0000", lineheight = 0.9)
  }
  if (no_x) {
    p <- p + theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank())
  }
  if (no_y) {
    p <- p + theme(axis.title.y=element_blank(), axis.text.y=element_blank(), axis.ticks.y=element_blank())
  }
  return(p)
}

include_colours = FALSE
p1 <- plot_to_45("polypolish_errors", "Polypolish-default", FALSE, FALSE, include_colours)
p2 <- plot_to_45("pypolca_errors", "Pypolca-default", FALSE, TRUE, include_colours)
p3 <- plot_to_45("polypolish_careful_errors", "Polypolish-careful", FALSE, FALSE, include_colours)
p4 <- plot_to_45("pypolca_careful_errors", "Pypolca-careful", FALSE, TRUE, include_colours)
p5 <- plot_to_45("fmlrc2_errors", "FMLRC2", FALSE, FALSE, include_colours)
p6 <- plot_to_45("hypo_errors", "HyPo", FALSE, TRUE, include_colours)
p7 <- plot_to_45("nextpolish_errors", "NextPolish", FALSE, FALSE, include_colours)
p8 <- plot_to_45("pilon_errors", "Pilon", FALSE, TRUE, include_colours)

jpeg(file = paste(plot_dir, "Figure2.jpeg", sep = "/" ), units = "in",
     width = 10,
     height = 12, bg = "transparent", res = 600)

plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, nrow=4, align = 'hv')
dev.off()

include_colours = TRUE
p1 <- plot_to_45("polypolish_errors", "Polypolish-default", FALSE, FALSE, include_colours)
p2 <- plot_to_45("pypolca_errors", "Pypolca-default", FALSE, TRUE, include_colours)
p3 <- plot_to_45("polypolish_careful_errors", "Polypolish-careful", FALSE, FALSE, include_colours)
p4 <- plot_to_45("pypolca_careful_errors", "Pypolca-careful", FALSE, TRUE, include_colours)
p5 <- plot_to_45("fmlrc2_errors", "FMLRC2", FALSE, FALSE, include_colours)
p6 <- plot_to_45("hypo_errors", "HyPo", FALSE, TRUE, include_colours)
p7 <- plot_to_45("nextpolish_errors", "NextPolish", FALSE, FALSE, include_colours)
p8 <- plot_to_45("pilon_errors", "Pilon", FALSE, TRUE, include_colours)

jpeg(file = paste(plot_dir, "Supp_Figure3.jpeg", sep = "/" ), units = "in",
     width = 10,
     height = 12, bg = "transparent", res = 600)

plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, nrow=4, align = 'hv')
dev.off()
```

Count introduced per interval

```{r overall per interval}

print("Polypolish default per genome introduction - at least 1/9")
table(total_results$polypolish_introduced)

print("Polypolish careful per genome introduction - at least 1/9")
table(total_results$polypolish_careful_introduced)

print("Pypolca default per genome introduction - at least 1/9")
table(total_results$pypolca_introduced)

print("Pypolca default per genome introduction - at least 1/9")
table(total_results$pypolca_careful_introduced)

print("HyPo per genome introduction - at least 1/9")
table(total_results$hypo_introduced)

print("Pilon per genome introduction - at least 1/9")
table(total_results$pilon_introduced)

print("Nextpolish per genome introduction - at least 1/9")
table(total_results$nextpolish_introduced)

print("FMLRC2 per genome introduction - at least 1/9")
table(total_results$fmlrc2_introduced)

```


Count introduced per genome

```{r overall per genome}

print("Polypolish default per genome introduction - at least 1/9")
table(introduced$Polypolish_introduced)

print("Polypolish careful per genome introduction - at least 1/9")
table(introduced$`Polypolish-careful_introduced`)

print("Pypolca default per genome introduction - at least 1/9")
table(introduced$pypolca_introduced)

print("Pypolca default per genome introduction - at least 1/9")
table(introduced$`pypolca-careful_introduced`)

print("HyPo per genome introduction - at least 1/9")
table(introduced$HyPo_introduced)

print("Pilon per genome introduction - at least 1/9")
table(introduced$Pilon_introduced)

print("Nextpolish per genome introduction - at least 1/9")
table(introduced$NextPolish_introduced)

print("FMLRC2 per genome introduction - at least 1/9")
table(introduced$FMLRC2_introduced)

```


```{r polypolish_pypolca_combinations, fig.width = 10, fig.height = 12}
p1 <- plot_to_45("polypolish_pypolca_errors", "Polypolish-default + Pypolca-default", FALSE, FALSE)
p2 <- plot_to_45("pypolca_polypolish_errors", "Pypolca-default + Polypolish-default", FALSE, TRUE)
p3 <- plot_to_45("polypolish_careful_pypolca_errors", "Polypolish-careful + Pypolca-default", TRUE, FALSE)
p4 <- plot_to_45("pypolca_polypolish_careful_errors", "Pypolca-default + Polypolish-careful", TRUE, TRUE)
p5 <- plot_to_45("polypolish_pypolca_careful_errors", "Polypolish-default + Pypolca-careful", FALSE, FALSE)
p6 <- plot_to_45("pypolca_careful_polypolish_errors", "Pypolca-careful + Polypolish-default", FALSE, TRUE)
p7 <- plot_to_45("polypolish_careful_pypolca_careful_errors", "Polypolish-careful + Pypolca-careful", FALSE, FALSE)
p8 <- plot_to_45("pypolca_careful_polypolish_careful_errors", "Pypolca-careful + Polypolish-careful", FALSE, TRUE)

jpeg(file = paste(plot_dir, "Supp_Figure5.jpeg", sep = "/" ), units = "in",
     width = 10,
     height = 12, bg = "transparent", res = 600)

plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, nrow=4, align = 'hv')
dev.off()
```

Plot the single polishers with their full range:

```{r plot_full_range, fig.width = 10, fig.height = 12}
plot_full_range <- function(column_name, polisher_name, no_x = FALSE, no_y = FALSE, include_colour = FALSE) {
  if (include_colour) {
    colours <- scale_colour_manual(values = c("TRUE" = "#CC0000", "FALSE" = "#127EAD"))
  } else {
    colours <- scale_colour_manual(values = c("TRUE" = "#662929", "FALSE" = "#662929"))
  }
  introduced_column <- gsub("_errors", "_introduced", column_name)
  max_y <- max(total_results[[column_name]], na.rm = TRUE) * 1.05
  p <- ggplot(total_results, aes(x=depth,y=!!sym(column_name),colour=!!sym(introduced_column) )) +
    geom_hline(yintercept = 37, color="#3A3A3A", linetype = "dashed") +
    geom_point(size=1.25) + colours +
    theme_bw() + theme(legend.position = "none") +
    scale_x_continuous(limits = c(0, 50), expand = c(0, 0)) +
    scale_y_continuous(limits = c(0, max_y), expand = c(0, 0)) +
    labs(title=polisher_name, x="Illumina depth", y="Errors")
  if (no_x) {
    p <- p + theme(axis.title.x=element_blank(), axis.text.x=element_blank(), axis.ticks.x=element_blank())
  }
  if (no_y) {
    p <- p + theme(axis.title.y=element_blank())
  }
  return(p)
}

p1 <- plot_full_range("polypolish_errors", "Polypolish-default", FALSE, FALSE, include_colour=FALSE)
p2 <- plot_full_range("pypolca_errors", "Pypolca-default", FALSE, TRUE,include_colour=FALSE)
p3 <- plot_full_range("polypolish_careful_errors", "Polypolish-careful", FALSE, FALSE,include_colour=FALSE)
p4 <- plot_full_range("pypolca_careful_errors", "Pypolca-careful", FALSE, TRUE,include_colour=FALSE)
p5 <- plot_full_range("fmlrc2_errors", "FMLRC2", FALSE, FALSE,include_colour=FALSE)
p6 <- plot_full_range("hypo_errors", "HyPo", FALSE, TRUE,include_colour=FALSE)
p7 <- plot_full_range("nextpolish_errors", "NextPolish", FALSE, FALSE,include_colour=FALSE)
p8 <- plot_full_range("pilon_errors", "Pilon", FALSE, TRUE,include_colour=FALSE)



jpeg(file = paste(plot_dir, "Supp_Figure2.jpeg", sep = "/" ), units = "in",
     width = 10,
     height = 12, bg = "transparent", res = 600)


plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, nrow=4, align = 'hv')

dev.off()

```

For each individual polisher, count how many times it made an input assembly better/worse and draw a stacked-bar plot:
```{r better_or_worse, fig.width = 8, fig.height = 4.5}
count_results <- function(tool_name, data) {
  tibble(
    Tool = tool_name,
    better = nrow(data %>% filter(!!sym(tool_name) < before_polish)),
    same = nrow(data %>% filter(!!sym(tool_name) == before_polish)),
    worse = nrow(data %>% filter(!!sym(tool_name) > before_polish))
  )
}

made_better_or_worse <- map_dfr(c("Polypolish", "Polypolish-careful", "pypolca", "pypolca-careful", "HyPo", "FMLRC2", "NextPolish", "Pilon"),
                                count_results, data = per_genome_results)

made_better_or_worse <- made_better_or_worse %>%
  pivot_longer(cols = -Tool, names_to = "Outcome", values_to = "Count") %>%
  mutate(Outcome = factor(Outcome, levels = c("better", "same", "worse"))) %>%
  mutate(Tool = factor(Tool, levels = c("pypolca", "pypolca-careful", "Polypolish", "Polypolish-careful", "FMLRC2", "HyPo", "NextPolish", "Pilon")))

# Create the stacked-bar plot
ggplot(made_better_or_worse, aes(x = Tool, y = Count, fill = Outcome)) +
  geom_bar(stat = "identity") +
  labs(title = "Per-genome polishing result", x = NULL, y = "Genome count") +
  theme_bw() + theme(legend.title=element_blank()) +
  scale_fill_manual(values = c("better" = "#74add1",
                               "same" = "#ffffbf",
                               "worse" = "#f46d43")) +
  scale_y_continuous(expand = c(0, 0)) + 
  scale_x_discrete(labels = c("pypolca-\ndefault", "pypolca\n-careful", "Polypolish-\ndefault", "Polypolish-\ncareful", "FMLRC2", "HyPo", "NextPolish", "Pilon"))
```

For each depth range (groups of 10x), determine which polisher/combination gave the best overall results:
```{r depth_groups}
best_by_depth_range <- function(total_results, min_depth, max_depth) {
  results_by_depth <- total_results %>% filter(depth > min_depth & depth <= max_depth)
  results_by_depth <- results_by_depth
  best_results <- results_by_depth %>%
    select(-depth) %>%
    summarise_all(sum) %>%
    pivot_longer(cols = everything(), names_to = "tool", values_to = "sum") %>%
    filter(sum == min(sum))
  return(best_results$tool)
}

interval <- 10
for (min_depth in seq(0, 45, interval)) {
  max_depth <- min_depth + interval
  best_tools <- best_by_depth_range(total_results, min_depth, max_depth)
  best_tools <- paste(best_tools, collapse = ", ")
  best_tools <- str_replace_all(best_tools, "_errors", "")
  cat(min_depth, "-", max_depth, ": ", best_tools, "\n", sep="")
}
```


What is the lowest depth that the polishers don't introduce errors?

```{r}

# Function to find the first row where value is 37 or lower for a given column
# at least 2x
find_first_row_below_threshold <- function(data, column_name, threshold) {
  first_row <- which(total_results[[column_name]][21:500] <= threshold)[1]  # Find the first row where value is <= threshold
  if (is.na(first_row)) {
    message("No rows found below threshold for column ", column_name)
    return(NA)
  } else {
    first_row <- first_row + 20 # to make up for the 20 offset
   cat("The lowest value of coverage for ", column_name ,  " where errors is equal or below", threshold, " is:", total_results$depth[first_row], "\n")
} 
    return(first_row)
  }
  

# Example usage
column_name <- "hypo_errors"  # Specify the column name
threshold <- 37  # Specify the threshold

first_row <- find_first_row_below_threshold(data, "pypolca_errors", threshold)
first_row <- find_first_row_below_threshold(data, "fmlrc2_errors", threshold)
first_row <- find_first_row_below_threshold(data, "hypo_errors", threshold)
first_row <- find_first_row_below_threshold(data, "nextpolish_errors", threshold)
first_row <- find_first_row_below_threshold(data, "pilon_errors", threshold)





```



```{r}
find_last_row_above_threshold <- function(data, column_name, threshold) {
  last_row <- max(which(total_results[[column_name]] > threshold))  # Find the last row where value is > threshold
  if (is.na(last_row)) {
    message("No rows found above threshold for column ", column_name)
    return(NA)
  } else {
   cat("The highest value of coverage for ", column_name ,  " where errors is equal or above", threshold, " is:", total_results$depth[last_row], "\n")
    return(last_row)
  }
}

# Example usage
column_name <- "hypo_errors"  # Specify the column name
threshold <- 37  # Specify the threshold

last_row <- find_last_row_above_threshold(data, "pypolca_errors", threshold)
last_row <- find_last_row_above_threshold(data, "fmlrc2_errors", threshold)
last_row <- find_last_row_above_threshold(data, "hypo_errors", threshold)
last_row <- find_last_row_above_threshold(data, "nextpolish_errors", threshold)
last_row <- find_last_row_above_threshold(data, "pilon_errors", threshold)
```


Get mean min max errors from 25+ for single polishers
```{r}

total_results %>%  filter(depth >= 25)


total_results %>%  filter(depth >= 25) %>% 
  pivot_longer(cols = before_polish:pilon_errors,
               names_to = "polisher", values_to = "value") %>%
  group_by(polisher) %>%
  summarize(
    mean_errors = mean(value, na.rm = TRUE),
    median_errors = median(value, na.rm = TRUE),
    sd_errors = sd(value, na.rm = TRUE),
    min_errors = min(value, na.rm = TRUE),
    max_errors = max(value, na.rm = TRUE),
    improvements = sum(value < 37, na.rm = TRUE),
    worse = sum(value > 37, na.rm = TRUE),
    equal = sum(value == 37, na.rm = TRUE),
  )


```


Get the means by each 5x depth bin for the 3 best polishers (Table 3)

```{r}

df_subset <- total_results[, c("depth","polypolish_careful_errors", "pypolca_careful_errors", "polypolish_errors")]

errors_by_bin <- df_subset %>%  
  filter(depth >= 0 ) %>% 
  mutate(bin = cut(depth, breaks = seq(0, max(depth) + 5, by = 5), include.lowest = TRUE)) %>%
  pivot_longer(cols = polypolish_errors:polypolish_careful_errors,
               names_to = "polisher", values_to = "value") %>%
  group_by(polisher, bin) %>%
  summarize(
    mean_errors = mean(value, na.rm = TRUE),
    median_errors = median(value, na.rm = TRUE),
    sd_errors = sd(value, na.rm = TRUE),
    min_errors = min(value, na.rm = TRUE),
    max_errors = max(value, na.rm = TRUE),
    improvements = sum(value < 37, na.rm = TRUE),
    worse = sum(value > 37, na.rm = TRUE),
    equal = sum(value == 37, na.rm = TRUE),
  )

errors_by_bin %>%  view()



```


Get mean min max errors from 25+ for combination polishers
```{r}




total_results %>%  filter(depth >= 25) %>% 
  pivot_longer(cols = polypolish_pypolca_errors:pypolca_polypolish_careful_errors,
               names_to = "polisher", values_to = "value") %>%
  group_by(polisher) %>%
  summarize(
    mean_errors = mean(value, na.rm = TRUE),
    median_errors = median(value, na.rm = TRUE),
    sd_errors = sd(value, na.rm = TRUE),
    min_errors = min(value, na.rm = TRUE),
    max_errors = max(value, na.rm = TRUE),
    improvements = sum(value < 37, na.rm = TRUE),
    worse = sum(value > 37, na.rm = TRUE),
    equal = sum(value == 37, na.rm = TRUE),
  )




```

Get the means by each 5x depth bin

```{r}

errors_by_bin <- total_results %>%  filter(depth >= 0 ) %>% 
  mutate(bin = cut(depth, breaks = seq(0, max(depth) + 5, by = 5), include.lowest = TRUE)) %>%
  pivot_longer(cols = polypolish_pypolca_errors:pypolca_polypolish_careful_errors,
               names_to = "polisher", values_to = "value") %>%
  group_by(polisher, bin) %>%
  summarize(
    mean_errors = mean(value, na.rm = TRUE),
    median_errors = median(value, na.rm = TRUE),
    sd_errors = sd(value, na.rm = TRUE),
    min_errors = min(value, na.rm = TRUE),
    max_errors = max(value, na.rm = TRUE),
    improvements = sum(value < 37, na.rm = TRUE),
    worse = sum(value > 37, na.rm = TRUE),
    equal = sum(value == 37, na.rm = TRUE),
  )

# keep only the 4 best with pypolca careful
pyolca_careful <- errors_by_bin %>% filter( grepl ("pypolca_careful", polisher) )

pyolca_careful %>%  view()
```
